---
title: "ps5"
author: "Hangyu Huang"
date: "17 October 2017"
output: 
  pdf_document: 
    keep_tex: yes
    number_sections: yes
---


## Partner
YUE HU

## Problem 2
In this problem, the double precision floating point representations for some integers from 2^0 to 2^53 are shown.

From 2^53 to 2^54, the spacing between integers that can be represented exactly is 2.

From 2^54 to 2^55, the spacing between integers that can be represented exactly is 4.
```{r Q1}
library(pryr)
bits(2^53-1)
bits(2^53)
bits(2^53+1)
bits(2^53+2)
bits(2^54)
bits(2^54+1)
bits(2^54+2)
bits(2^54+3)
bits(2^54+4)
```
1: (-1)^0 x 1 x (2)^(1023-1023)

2: (-1)^0 x 1 x (2)^(1024-1023)

3: (-1)^0 x (1.1) x (2)^(1024-1023)

2^53-2:(-1)^0 x (1.11...111110) x (2)^(1075-1023) # 11...11111: total 51 "1"

2^53-1:(-1)^0 x (1.11...11111) x (2)^(1075-1023) # 11....111111: total 52 "1"

2^53: (-1)^0 x (1) x (2)^(1076-1023)

2^53+2: (-1)^0 x (1.000....00001) x (2)^(1076-1023) #000...0000: total 51 "0"

As the fraction has only 52bits, 

From 2^52 to 2^53, the representable numbers are exactly the integers,total 2^52 number of 
intergers;

From 2^53 to 2^54, everything is multipulied by 2, so the representable numbers are all the even numbers, the spacing is 2, such as 2^53 = (2^52)x2, 2^53+2=(2^52+1)x2. Therefore, 2^53+1 cannot be represented,

From 2^54 to 2^55, everything is multipulied by 2^2=4, so the representable numbers are the numbers with spacing 4, such as 2^54 = (2^52)x4, 2^54+4= (2^52+1)x4. 

## Problem 3
(a) "system.time()"is used to compare the time used of copying a large vector of integers to the time of copying a large vector of numeric numbers. 

Based on the results, it can be concluded that it is faster to copy a large vector of integers than a numeric vector of the same length in R.

(b) Based on the results, it can be concluded that it is slightly faster to take a subset of size k ??? n/2 from an integer vector of size n than from a numeric vector of size n.

```{r problem 3a}
#integer case
Int<- c(1:1e8)
object.size(Int)
IntNew <- Int  
print(system.time(IntNew[40] <- 10L)) 
# As Intnew is now different to Int, a real vevtor of integers copy is made.
print(system.time(IntNew[1:5e7])) 
#it shows the time to take a subset of size k=n/2 from an integer vector.

# numeric case 
Numrc <- Int
print(system.time(Numrc[40] <- 10)) 
# As Numrc is now different to Int, a real vevtor of numeric numbers copy is made.
print(system.time(Numrc[1:5e7])) 
# it shows the time to take a subset of size k=n/2 from a numeric vector of size n.
```
## Problem 4
(a)

Both memory usage and the ammount of communication need to be considered. In this case, for many tasks that each take similar time, you want to preschedule the tasks to reduce communication. However, the communication overhead of starting and stopping the task will reduce efficiency.

(b)

Approach A: 

Memory Usage: 

Each worker will use X (n x n) and submatrix of Y (n x m) with a result of nxm.

For P wokers, the total memory is P x (n^2+2nm)

Amount of Communication:

P x (n^2+2mn) = nnp + 2nn

Approach B: 

Memory Usage: 

Each worker will use X (m x n) and submatrix of Y (n x m) with a result of nxm.
For P wokers, the total memory is P x (2nm+m^2)
Amount of Communication:
(P x P)x (m^2+2mn) =nn +2pnn

Based on the result, we can see that B uses less memory than A, however, A takes less Commication cost than B.

In conclusion, Approch A is better for minimizing communication, Approach B is better for minimizing memory.