---
title: "ps4"
author: "Hangyu Huang"
date: "10 October 2017"
output: 
  pdf_document: 
    number_sections: yes
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Partner

Partner: YUE HU

## Problem 1(a)
There is only one copy that exists of the vector 1:10 during the first execution of myFun(). 
Based on the idea of copy on change, 
copies of objects are not made until one of the objects is actually modified. 
Since there is no change on vector 1:10, 
"data" points to the same memory location as the original object "x". 

## Problem 1(b)
The serialized object size is actually twice of the size of object "x".
It seems like that the function "serialize" serialized both "x" and "data" to a raw vector as this function can not recognize that "x" and "data" point to the same memory location.

```{r problem 1 (b)}
x <- 1:1e7 
f <- function(input){ 
        data <- input 
        g <- function(param) return(param * data) 
        return(g) 
        } 
myFun <- f(x) 
bytes <- serialize(myFun,NULL)
print(object.size(x))
print(object.size(bytes))
```

## Problem 1 (c)
Based on "lazy evaluation", when R matches user input arguments to formal argument names, 
it does not (usually) evaluate the arguments until they are needed. 

In this question, "x" is not copied until "myFun" is called at "myFun(3)", 
however "x" has been already removed. 
Therefore, R cannot find object 'x'.

## Problem 1 (d)
The resulting serialized closure is 888 bytes
```{r problem 1 (d)}
x <- 1:10 
f <- function(data){ 
        g <- function(param) return(param * data) 
        return(g) 
        } 
myFun <- f(1:10) 
rm(x) 
data <- 100 
myFun(3)
bytes <- serialize(myFun,NULL)
print(object.size(bytes))
```

## problem 2 (a)
When an element of one of the vectors is modified, 
R makes the change in place without creating a new list or a new vector.

From the result, we can see that 2 vectors are in the same place. 
```{r problem 2 (a)}
library(pryr)
tmp <- list(rnorm(1e7), rnorm(1e7))
.Internal(inspect(tmp)) 
mem_change(tmp[[1]][1] <- 1 )
.Internal(inspect(tmp))
```
## problem 2 (b)
There is no copy-on-change going on when I make a copy of the list. However, a copy of the relevant vector is made when a change is made to one of the vectors in one of the lists.

From the result we can find that only the place of vector [1] of "copyofTmp" is changed and the memory is increased almost 80Mb, which is the size of one vector.
```{r problem 2 (b)}
library(pryr)
mem_change(copyofTmp <- tmp)
.Internal(inspect(tmp)) 
.Internal(inspect(copyofTmp)) 
mem_change(copyofTmp[[1]][1] <- 2 )
.Internal(inspect(tmp)) 
.Internal(inspect(copyofTmp))
```
## problem 2 (c)
When the copy of a list of lists "lists", "copyofLists" is made, there is no copy-on-change going on. The two lists point to the same memory location.

When an element is added to the second list, only one copy of the new vector is made for "copyofLists$B", there is no change for the rest of the two lists. 30Mb memory change takes place, which is the size of the added element.

```{r problem 2 (c)}
library(pryr)
lists <- list(A = list(a = rnorm(1e7), b = rnorm(1e7)),
              B = list(a = rnorm(1e6)))
mem_change(copyofLists <- lists)
.Internal(inspect(lists)) 
.Internal(inspect(copyofLists)) 
mem_change(copyofLists$B <- c(copyofLists$B, rnorm(1e6)))
.Internal(inspect(lists)) 
.Internal(inspect(copyofLists))
```

## problem 2 (d)
We find that the two vectors in the list point to the memory location. so the real memory used is ~80Mb as can be seen with gc().

object.size():This function merely provides a rough indication: it should be reasonably accurate for atomic vectors, but does not detect if elements of a list are shared, for example. 

Therefore, object.size() count the memory of both elements in the list, which is two times of the real size.
``` {r problem 2 (d)}
gc() 
tmp <- list()
x <- rnorm(1e7) 
tmp[[1]] <- x 
tmp[[2]] <- x 
.Internal(inspect(tmp)) 
object.size(tmp) 
gc()
```

## problem 3 original code
To present the time the original code takes.

```{r problem 3 original code}
library(rbenchmark)
load("C:/Users/crypress/Desktop/243/ps4prob3.Rda") # provides values for A, k, n
ll <- function(Theta, A) {
  sum.ind <- which(A==1, arr.ind=T)
  logLik <- sum(log(Theta[sum.ind])) - sum(Theta)
  return(logLik)
}
oneUpdate <- function(A, n, K, theta.old, thresh = 0.1) {
  theta.old1 <- theta.old
  Theta.old <- theta.old %*% t(theta.old)
  L.old <- ll(Theta.old, A)
  q <- array(0, dim = c(n, n, K))
  for (i in 1:n) {
    for (j in 1:n) {
      for (z in 1:K) {
        if (theta.old[i, z]*theta.old[j, z] == 0){
          q[i, j, z] <- 0
        } else {
          q[i, j, z] <- theta.old[i, z]*theta.old[j, z] /
            Theta.old[i, j]
        }
      }
    }
  }
  theta.new <- theta.old
  for (z in 1:K) {
    theta.new[,z] <- rowSums(A*q[,,z])/sqrt(sum(A*q[,,z]))
  }
  Theta.new <- theta.new %*% t(theta.new)
  L.new <- ll(Theta.new, A)
  converge.check <- abs(L.new - L.old) < thresh
  theta.new <- theta.new/rowSums(theta.new)
  return(list(theta = theta.new, loglik = L.new,
              converged = converge.check))
}
# initialize the parameters at random starting values
temp <- matrix(runif(n*K), n, K)
theta.init <- temp/rowSums(temp)
# do single update and check the time
print(system.time(out <- oneUpdate(A, n, K, theta.init)))
```

## problem 3 improved code
To present the time the improved code takes.
```{r problem 3 improved code}
load("C:/Users/crypress/Desktop/243/ps4prob3.Rda") # provides values for A, k, n
# change the name of the function from "ll" to "getlogLik" to show the application of this function
getlogLik <- function(Theta, A) {
  sum.ind <- which(A==1, arr.ind=T)
  logLik <- sum(log(Theta[sum.ind])) - sum(Theta)
  return(logLik)
}
oneUpdate <- function(A, n, K, theta.old, thresh = 0.1) {
  # theta.old1 is removed as it is not used in the funtion
  Theta.old <- theta.old %*% t(theta.old)
  L.old <- getlogLik(Theta.old, A)
  # instead of 3 dimentional array, a  2-D matrix is used to for q
  q <- matrix(0, nrow = n,ncol = n)
  theta.new <- theta.old
  # instead of using a for loop, apply() is applied here
  theta.new<- apply(matrix(1:K), 1, FUN = function(z) {
    q <- theta.old[,z]%*% t(theta.old[,z])/Theta.old
    theta.new[,z] <- rowSums(A*q)/sqrt(sum(A*q))
  })
  Theta.new <- theta.new %*% t(theta.new)
  L.new <- getlogLik(Theta.new, A)
  converge.check <- abs(L.new - L.old) < thresh
  theta.new <- theta.new/rowSums(theta.new)
  return(list(theta = theta.new, loglik = L.new,
              converged = converge.check))
}
# initialize the parameters at random starting values
temp <- matrix(runif(n*K), n, K)
theta.init <- temp/rowSums(temp)
# do single update and check the time
out <- oneUpdate(A, n, K, theta.init)
print(system.time(out <- oneUpdate(A, n, K, theta.init)))

```
## problem 4 (a) PIKK algorithm

```{R problem 4 PIKK algorithm}
# PIKK algorithm
library(microbenchmark)
PIKK <- function(x, k) {
  sort(runif(length(x)), 
         index.return = TRUE)$ix[1:k]
}

# improved PIKK algorithm
newPIKK <- function(x, k) {
  order(runif(length(x)))[1:k]
}

# test and compare 
orgTime <- list()
newTime <- list()
n <- c(0,1e2,1e3,1e4, 1e5)
for (i in n){
  x <- c(1:i)
  k <- i/100
  orgBenchm <- microbenchmark(PIKK(x,k))
  newBenchm <- microbenchmark(newPIKK(x,k))
  orgTime <- c(orgTime, mean(orgBenchm$time))
  newTime<- c(newTime, mean(newBenchm$time))
}
plot(n,orgTime, type = "l", col = "red",
     xlab = "n", ylab ="time")
lines(n, newTime, col = "blue")
```

## Problem 4 (b) PYKD algorithm

```{R problem 4 PYKD algorithm}
# original FYKD algorithm
FYKD <- function(x, k) { 
  n <- length(x)
  for(i in 1:k) {
    j = sample(i:n, 1)
    tmp <- x[i]
    x[i] <- x[j]
    x[j] <- tmp
  }
  return(x[1:k])
}
    

# Improved FYKD algorithm
newFYKD <- function(x, k) { 
  n <- length(x)
  y <- c(1:k)
  idx <- sapply(y, function(x){
    sample(i:n,1)})
  for(i in 1:k) {
    tmp <- x[i]
    x[i] <- x[idx[i]]
    x[idx[i]] <- tmp
  }
  return(x)
}
# test and compare 
orgTime <- list()
newTime <- list()
n <- c(1e2,1e3,1e4, 1e5)
for (i in n){
  x <- c(1:i)
  k <- i/100
  orgBenchm <- microbenchmark(FYKD(x,k))
  newBenchm <- microbenchmark(newFYKD(x,k))
  orgTime <- c(orgTime, mean(orgBenchm$time))
  newTime<- c(newTime, mean(newBenchm$time))
}
plot(n,orgTime, type = "l", col = "red",
     xlab = "n", ylab ="time")
lines(n, newTime, col = "blue")
```